Fractional Types

### 2019-11-20 fracGC/p.tex
Add some code to sec 4
try to put all the needed code in paper (WIP)
Code for extraction
code for MemSem

\newunicodechar{𝕌}{$\mathbb{U}$}
\newunicodechar{𝔹}{$\mathbb{B}$}
\newunicodechar{𝔽}{$\mathbb{F}$}
\newunicodechar{𝕋}{$\mathbb{T}$}
\newunicodechar{𝟘}{$\mathbb{0}$}
\newunicodechar{𝟙}{$\mathbb{1}$}
\newunicodechar{𝟚}{$\mathbb{2}$}
\newunicodechar{⋆}{${}_*$}
\newunicodechar{○}{$\gcv$}
\newunicodechar{ᵤ}{${}_u$}
\newunicodechar{⊚}{$\fatsemi$}
\newunicodechar{⟷}{$\leftrightarrow$}

@@

\input{latex/PiFracDynCode.tex}
\input{latex/BooleanCircuitsCode.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

The step from reversible classical circuits to quantum circuits
requires the addition of just one gate that creates
superpositions. Similarly the step from a reversible classical
programming language to a quantum one requires just the management of
superpositions, for example starting from the classical reversible
language Theseus~\cite{XXX}, a small extension produces a quantum
language with quantum control~\cite{10.1007/978-3-319-89366-2_19}. The
language Theseus~\cite{XXX} mentioned above is a language that uses
convenient syntactic extensions over an more basic language $\Pi$ of
combinators witnessing isomorphisms over finite types~\cite{XXX}. The
combinator-based language has the advantage of being more amenable to
formal analysis for at least two reasons: (i) it is conceptually
simple and small, and (ii) it has direct and evident connections to
type theory and category theory. Indeed our solution for managing
ancillae is inspired by the construction of \emph{compact closed
  categories}~\cite{XXX}. These categories extend the monoidal
categories~\cite{XXX} which are used to model many resource-aware
programming languages~\cite{XXX} (including $\Pi$) with a new type
constructor that creates duals or inverses to existing types. This
dual will be our fractional type.

@@

@@

@@

@@

@@

>>>>

\newunicodechar{𝕌}{$\mathbb{U}$}
\newunicodechar{𝔹}{$\mathbb{B}$}
\newunicodechar{𝔽}{$\mathbb{F}$}
\newunicodechar{𝕋}{$\mathbb{T}$}
\newunicodechar{𝟘}{$\mathbb{0}$}
\newunicodechar{𝟙}{$\mathbb{1}$}
\newunicodechar{𝟚}{$\mathbb{2}$}
\newunicodechar{⋆}{${}_*$}
\newunicodechar{○}{$\gcv$}
\newunicodechar{ᵤ}{${}_u$}
\newunicodechar{⊚}{$\fatsemi$}
\newunicodechar{⟷}{$\leftrightarrow$}
\newunicodechar{⟶}{$\longrightarrow$}
\newunicodechar{⟪}{$\ll$}
\newunicodechar{⟫}{$\gg$}

@@

\input{latex/PiFracDynDefCode.tex}
\input{latex/PiFracDynCode.tex}
\input{latex/BooleanCircuitsCode.tex}
\input{latex/PiPointedFracCode.tex}
\input{latex/ExtractionCode.tex}
\input{latex/PiMemSemCode.tex}
\input{latex/PiFracMemSemCode.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

The step from reversible classical circuits to quantum circuits
requires the addition of just one gate that creates
superpositions. Similarly the step from a reversible classical
programming language to a quantum one requires just the management of
superpositions, for example starting from the classical reversible
language Theseus~\cite{james2014theseus}, a small extension produces a quantum
language with quantum control~\cite{10.1007/978-3-319-89366-2_19}. The
language Theseus~\cite{james2014theseus} mentioned above is a language that uses
convenient syntactic extensions over an more basic language $\Pi$ of
combinators witnessing isomorphisms over finite types~\cite{XXX}. The
combinator-based language has the advantage of being more amenable to
formal analysis for at least two reasons: (i) it is conceptually
simple and small, and (ii) it has direct and evident connections to
type theory and category theory. Indeed our solution for managing
ancillae is inspired by the construction of \emph{compact closed
  categories}~\cite{XXX}. These categories extend the monoidal
categories~\cite{XXX} which are used to model many resource-aware
programming languages~\cite{XXX} (including $\Pi$) with a new type
constructor that creates duals or inverses to existing types. This
dual will be our fractional type.

@@

\PIFDUdef{}

change of combinators:
\PIFDCombdef{}

change of interpreter:
\PIFDinterp{}

@@

\PIPFUdef{}

@@

Combinators:
\PIPFCombDef{}

Evaluation:
\PIPFeval{}

Combine with eval, the whole thing is reversible:
\PIPFrev{}

\subsection{Extraction}

@@

Inject plain Pi into PiFracDyn:
\INJU{}
The injection is correct:
\INJeq{}
Extract type from PiPointedFrac:
\EXTU{}
Extract combinator:
\EXTUComb{}
The extraction is correct:
\EXTeq{}

@@

cardinality of pi type:
\PIMEMcard{}
enumeration:
\PIMEMenum{}
combinator preserve size:
\PIMEMcardeq{}
semantics for Pi:
\PIMEMstate{}
\PIMEMstep{}
semantics for PiFracDyn:
\PIFMEMstate{}
\PIFMEMstep{}
